Displacement of fishing effort by Large Scale Marine Protected Areas\footnote{Work in progress, do not circulate}

### 2018-10-21 docs/Manuscript.tex
Updated manuscritp, sent to John

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{\label{fig:unnamed-chunk-13}\label{fig:LSMPAs_map}Large Scale
Marine Protected Areas. The map shows all areas larger than 250,000
Km\textsuperscript{2}. Areas in dark blue meet at least one of these
conditions: reported no take area is greater than 0, are categorized as
IUCN Ia or Ib, their designated english name is `Protected Area'.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
\caption{\label{fig:unnamed-chunk-14}\label{fig:PNA_map}Map of the Exclusive
Economic Zones (EEZs) of the region of interest. Countries that belong
to the PNA are shown in blue, while empty polygons indicates all others.
A red line indicates the Kiribati EEZ, and a solid red polygon
delineates PIPA.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-17}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Group & n & Before & After & Change (A / B)\\
\midrule
Control & 26 & 11.74 & 20.13 & 1.72\\
Treatment & 61 & 10.67 & 18.36 & 1.72\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
\caption{\label{fig:unnamed-chunk-18}\label{fig:all_vessels}Fishing hours
and number of vessels by month for all vessels. Vertical dashed lines
indicates dates when satellites were added, solid line indicates PIPA
closurePIPA closure.}
\end{figure}

@@

We use daily fishing hours, daily proportion of fishing vs.~non-fishing
hours, and daily distance traveled (km). We compare our variable of
interest before and after the implementation of PIPA using a
Difference-in-Differences approach, where we track the variable of
interest for vessels described in the previous section. Our
specification is the following:

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
\caption{\label{fig:unnamed-chunk-21}\label{fig:all_vessels}Daily fishing
hours for all vessels in our main treatment-control groups. Solid
straight lines show a linear trend by period (pre-psot) and treatment.
The other red and blue lines show monthly avarages. Vertical dashed
lines indicates dates when satellites were added, solid line indicates
PIPA closurePIPA closure.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
\caption{\label{fig:unnamed-chunk-23}\label{fig:long}Coefficient estimates
for each model. Top pannel indicates variable, x-axis represents model
specification, and y-axis coefficient estimate.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
\caption{\label{fig:unnamed-chunk-24}\label{fig:fishing_raster}Yearly
spatial distribution of fishing effort by treated and control vessels.
Colors have been adjusted relative to the maximum observed by group and
year. Red polygons show LGMPAs in the region. For visualization purpose
sonly some years are presented, the full 2012 - 2017 period is shown in
Figure \ref{fig:fishing_raster_full}.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
\caption{\label{fig:unnamed-chunk-25}\label{fig:redist_trend}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA by region. Colors indicate the pre-post period. Solid line
across points shows local mean with a region-specific loess smoother.
Vertical dashed lines indicates dates when satellites were added, solid
line indicates PIPA closurePIPA closure. Note that inflection points of
the loess smoother are not affected by the addition of satellites.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
\caption{\label{fig:unnamed-chunk-26}\label{fig:mean_change}Coefficient
estimates for the redistribution regression. Each pannel shows the
region-specific coefficients, with heteroskedastick-robust standard
errors as error bars. The horizontal dashed line represents 0 chenge
relative to the 2012 region-specific levels.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-27}\label{tab:mean_change}Coefficient estimates for the interaction of year and region. Each row represents a region, each color a year. Numbers in parentheses are heteroskedatic-robust standard errors. R2 = 0.47 (F(95, 1056) = 9.99; p < 0.001). * < 0.1; ** p < 0.05; ***p < 0.01.}
\centering
\begin{tabular}[t]{llllll}
\toprule
term & 2013 & 2014 & 2015 & 2016 & 2017\\
\midrule
PIPA PIPA 1 & -0.062 (0.026)** & 0.085 (0.043)** & -0.086 (0.026)*** & -0.079 (0.025)*** & -0.074 (0.025)***\\
EEZ KIR 1 & -0.034 (0.030) & 0.035 (0.038) & 0.042 (0.045) & -0.035 (0.031) & -0.023 (0.032)\\
EEZ KIR 2 & 0.001 (0.009) & 0.032 (0.019)* & 0.142 (0.061)** & 0.014 (0.013) & 0.014 (0.015)\\
EEZ KIR 3 & -0.188 (0.075)** & -0.061 (0.072) & -0.118 (0.069)* & -0.093 (0.083) & -0.098 (0.083)\\
HS KIR 1 & -0.003 (0.011) & 0.016 (0.012) & 0.038 (0.013)*** & 0.004 (0.013) & 0.037 (0.018)**\\
\addlinespace
HS KIR 2 & 0.009 (0.006) & 0.004 (0.006) & -0.000 (0.009) & 0.022 (0.010)** & 0.008 (0.006)\\
HS KIR 3 & -0.002 (0.009) & 0.003 (0.009) & -0.008 (0.011) & 0.022 (0.011)* & 0.064 (0.024)***\\
HS HS 1 & 0.021 (0.015) & 0.027 (0.017) & 0.045 (0.017)*** & 0.030 (0.017)* & 0.014 (0.015)\\
EEZ FSM 1 & 0.018 (0.033) & -0.015 (0.025) & 0.000 (0.037) & 0.012 (0.025) & -0.001 (0.021)\\
EEZ MHL 1 & 0.037 (0.022) & 0.025 (0.010)** & -0.006 (0.009) & 0.052 (0.032) & -0.000 (0.006)\\
\addlinespace
EEZ NRU 1 & 0.046 (0.021)** & 0.044 (0.020)** & 0.003 (0.017) & 0.033 (0.015)** & 0.050 (0.025)**\\
EEZ PNG 2 & 0.196 (0.072)*** & -0.106 (0.041)*** & -0.132 (0.043)*** & -0.064 (0.048) & 0.001 (0.049)\\
EEZ SLB 1 & 0.083 (0.056) & -0.019 (0.032) & -0.009 (0.038) & 0.081 (0.053) & 0.076 (0.046)*\\
EEZ TUV 1 & -0.055 (0.037) & -0.033 (0.040) & -0.063 (0.037)* & 0.018 (0.046) & -0.026 (0.038)\\
HS COK 1 & -0.003 (0.008) & -0.004 (0.008) & -0.003 (0.011) & -0.007 (0.008) & -0.003 (0.008)\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-28-1.pdf}
\caption{\label{fig:unnamed-chunk-28}\label{fig:sp_corr}Number of cells that
had treated and control vessels (A) and spatial correlation in the
presence-absence of treated and control vessels per cell (B).}
\end{figure}

@@

\begin{itemize}
\tightlist
\item
  Distance traveled
\item
  Non-fishing hours at sea
\item
  Monthly crowdnes??
\item
  Repeat raster exercise for Revillagigedo and other recently
  implemented LSMPAs. It would be great to have a pannel figure of 3 or
  4 other LSMPAs that show wher effort was and where it went to
  generalize our results.
\item
  John talked about this being relevant to Palau (their upcoming LSMPA).
  We might want to talk about where the vessels that are there would go.
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-29-1.pdf}
\caption{\label{fig:unnamed-chunk-29}\label{fig:baci_strict}Stream of
fishing events by vessels through time. Each line represents a vessel,
with dots indicating months with fishing activity and colors indicating
the pre and post periods.}
\end{figure}

@@

\hypertarget{other-model-specifications-for-purse-seiners}{%
\subsection{Other model specifications for purse
seiners}\label{other-model-specifications-for-purse-seiners}}

We include a second degree polynomial for years as:

\[
y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \omega Y_t + \Omega Y_t^2 + \epsilon_{i,t}
\]

\textbackslash{}begin\{table\}{[}!htbp{]} \centering 
\textbackslash{}caption\{\label{tab:purse}Fishing hours from GFW for
purse\_seiners. Asterisks indicate significance levels. Numbers in
parentheses represent heteroskedastic-robust standard errors.\} \label{}

\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & 8.394$^{***}$ & 9.334$^{***}$ & 14.934$^{***}$ & 17.284$^{***}$ \\ 
  & (0.267) & (0.254) & (0.312) & (0.403) \\ 
  & & & & \\ 
 treated & $-$1.069$^{***}$ & $-$0.770$^{***}$ & $-$0.993$^{***}$ & 0.259 \\ 
  & (0.249) & (0.234) & (0.219) & (0.269) \\ 
  & & & & \\ 
 post:treated & $-$0.701$^{**}$ & $-$0.899$^{***}$ & $-$0.530$^{*}$ & $-$0.580$^{**}$ \\ 
  & (0.308) & (0.295) & (0.283) & (0.292) \\ 
  & & & & \\ 
 Constant & 11.738$^{***}$ & 11.281$^{***}$ & 7.574$^{***}$ & 10.077$^{***}$ \\ 
  & (0.220) & (0.292) & (0.318) & (0.422) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Year FE & No & No & Yes & Yes \\ 
Flag FE & No & No & No & Yes \\ 
Observations & 37,840 & 37,840 & 37,840 & 37,840 \\ 
R$^{2}$ & 0.087 & 0.136 & 0.179 & 0.192 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular}

\textbackslash{}end\{table\}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-33-1.pdf}
\caption{\label{fig:unnamed-chunk-33}\label{fig:q1}Interaction of quarters
and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-34-1.pdf}
\caption{\label{fig:unnamed-chunk-34}\label{fig:q2}Interaction of quarters
and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-35-1.pdf}
\caption{\label{fig:unnamed-chunk-35}\label{fig:q3}Interaction of quarters
and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-36-1.pdf}
\caption{\label{fig:unnamed-chunk-36}\label{fig:q4}Interaction of quarters
and treatment. Control group is japanese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-1.pdf}
\caption{\label{fig:unnamed-chunk-37}\label{fig:ym1}Interaction of
year-month and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-1.pdf}
\caption{\label{fig:unnamed-chunk-38}\label{fig:ym2}Interaction of
year-month and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-39-1.pdf}
\caption{\label{fig:unnamed-chunk-39}\label{fig:ym3}Interaction of
year-month and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-40-1.pdf}
\caption{\label{fig:unnamed-chunk-40}\label{fig:ym4}Interaction of
year-month and treatment. Control group is japanese vessels.}
\end{figure}

@@

\hypertarget{rasterized-regions}{%
\subsection{Rasterized regions}\label{rasterized-regions}}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-41-1.pdf}
\caption{\label{fig:unnamed-chunk-41}\label{fig:raster_rgn}Rasterized
regions. Each color (number) indicates a distinct region.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
Protected Areas. The map shows all areas larger than 250,000
Km\textsuperscript{2}. Areas in dark blue meet at least one of these
conditions: reported no take area is greater than 0, are categorized as
IUCN Ia or Ib, their designated english name is `Protected Area'.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}Map of the Exclusive
Economic Zones (EEZs) of the region of interest. Countries that belong
to the PNA are shown in blue, while empty polygons indicates all others.
A red line indicates the Kiribati EEZ, and a solid red polygon
delineates PIPA.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Group & n & Before & After & Change (A / B)\\
\midrule
Control & 26 & 11.74 & 20.13 & 1.72\\
Treatment & 61 & 10.67 & 18.36 & 1.72\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
number of vessels by month for all vessels. Vertical dashed lines
indicates dates when satellites were added, solid line indicates PIPA
closurePIPA closure.}
\end{figure}

@@

We use daily fishing hours, daily proportion of fishing vs.~non-fishing
hours, daily distance traveled (km), distance from shore (km) and
distance from
port(km)\footnote{Results are presented for fishing hours, bur preliminary results for distance form shore and distance from port are shown in Tables \ref{tab:dist_shore} and \ref{tab:dist_port}}.
We compare our variable of interest before and after the implementation
of PIPA using a Difference-in-Differences approach, where we track the
variable of interest for vessels described in the previous section. Our
specification is the following:

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Daily fishing
hours for all vessels in our main treatment-control groups. Solid
straight lines show a linear trend by period (pre-psot) and treatment.
The other red and blue lines show monthly avarages. Vertical dashed
lines indicates dates when satellites were added, solid line indicates
PIPA closurePIPA closure.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{\label{fig:unnamed-chunk-12}\label{fig:long}Coefficient estimates
for each model. Top pannel indicates variable, x-axis represents model
specification, and y-axis coefficient estimate.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{\label{fig:unnamed-chunk-13}\label{fig:fishing_raster}Yearly
spatial distribution of fishing effort by treated and control vessels.
Colors have been adjusted relative to the maximum observed by group and
year. Red polygons show LGMPAs in the region. For visualization purpose
sonly some years are presented, the full 2012 - 2017 period is shown in
Figure \ref{fig:fishing_raster_full}.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA by region. Colors indicate the pre-post period. Solid line
across points shows local mean with a region-specific loess smoother.
Vertical dashed lines indicates dates when satellites were added, solid
line indicates PIPA closurePIPA closure. Note that inflection points of
the loess smoother are not affected by the addition of satellites.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
\caption{\label{fig:unnamed-chunk-15}\label{fig:mean_change}Coefficient
estimates for the redistribution regression. Each pannel shows the
region-specific coefficients, with heteroskedastick-robust standard
errors as error bars. The horizontal dashed line represents 0 chenge
relative to the 2012 region-specific levels.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-16}\label{tab:mean_change}Coefficient estimates for the interaction of year and region. Each row represents a region, each color a year. Numbers in parentheses are heteroskedatic-robust standard errors. R2 = 0.47 (F(95, 1056) = 9.99; p < 0.001). * < 0.1; ** p < 0.05; ***p < 0.01.}
\centering
\begin{tabular}[t]{llllll}
\toprule
term & 2013 & 2014 & 2015 & 2016 & 2017\\
\midrule
PIPA PIPA 1 & -0.062 (0.026)** & 0.085 (0.043)** & -0.086 (0.026)*** & -0.079 (0.025)*** & -0.074 (0.025)***\\
EEZ KIR 1 & -0.034 (0.030) & 0.035 (0.038) & 0.042 (0.045) & -0.035 (0.031) & -0.023 (0.032)\\
EEZ KIR 2 & 0.001 (0.009) & 0.032 (0.019)* & 0.142 (0.061)** & 0.014 (0.013) & 0.014 (0.015)\\
EEZ KIR 3 & -0.188 (0.075)** & -0.061 (0.072) & -0.118 (0.069)* & -0.093 (0.083) & -0.098 (0.083)\\
HS KIR 1 & -0.003 (0.011) & 0.016 (0.012) & 0.038 (0.013)*** & 0.004 (0.013) & 0.037 (0.018)**\\
\addlinespace
HS KIR 2 & 0.009 (0.006) & 0.004 (0.006) & -0.000 (0.009) & 0.022 (0.010)** & 0.008 (0.006)\\
HS KIR 3 & -0.002 (0.009) & 0.003 (0.009) & -0.008 (0.011) & 0.022 (0.011)* & 0.064 (0.024)***\\
HS HS 1 & 0.021 (0.015) & 0.027 (0.017) & 0.045 (0.017)*** & 0.030 (0.017)* & 0.014 (0.015)\\
EEZ FSM 1 & 0.018 (0.033) & -0.015 (0.025) & 0.000 (0.037) & 0.012 (0.025) & -0.001 (0.021)\\
EEZ MHL 1 & 0.037 (0.022) & 0.025 (0.010)** & -0.006 (0.009) & 0.052 (0.032) & -0.000 (0.006)\\
\addlinespace
EEZ NRU 1 & 0.046 (0.021)** & 0.044 (0.020)** & 0.003 (0.017) & 0.033 (0.015)** & 0.050 (0.025)**\\
EEZ PNG 2 & 0.196 (0.072)*** & -0.106 (0.041)*** & -0.132 (0.043)*** & -0.064 (0.048) & 0.001 (0.049)\\
EEZ SLB 1 & 0.083 (0.056) & -0.019 (0.032) & -0.009 (0.038) & 0.081 (0.053) & 0.076 (0.046)*\\
EEZ TUV 1 & -0.055 (0.037) & -0.033 (0.040) & -0.063 (0.037)* & 0.018 (0.046) & -0.026 (0.038)\\
HS COK 1 & -0.003 (0.008) & -0.004 (0.008) & -0.003 (0.011) & -0.007 (0.008) & -0.003 (0.008)\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
\caption{\label{fig:unnamed-chunk-17}\label{fig:sp_corr}Number of cells that
had treated and control vessels (A) and spatial correlation in the
presence-absence of treated and control vessels per cell (B).}
\end{figure}

@@

\begin{itemize}
\tightlist
\item
  Distance traveled
\item
  Non-fishing hours at sea
\item
  Monthly crowdnes (same approach as now, but monthly instead of yearly)
\item
  Number of vessels per cell as another measure of crowdness (this is a
  more real one)
\item
  Repeat raster exercise for Revillagigedo and other recently
  implemented LSMPAs. It would be great to have a pannel figure of 3 or
  4 other LSMPAs that show wher effort was and where it went to
  generalize our results.
\item
  John talked about this being relevant to Palau (their upcoming LSMPA).
  We might want to talk about where the vessels that are there would go.
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
fishing events by vessels through time. Each line represents a vessel,
with dots indicating months with fishing activity and colors indicating
the pre and post periods.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
\caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
\caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
and treatment. Control group is japanese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
\caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
year-month and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
\caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
year-month and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
\caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
year-month and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
\caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
year-month and treatment. Control group is japanese vessels.}
\end{figure}

\hypertarget{other-measures-of-change-in-behavior}{%
\subsection{Other measures of change in
behavior}\label{other-measures-of-change-in-behavior}}

Global Fishing Watch data includes two variables of interest that are
readily available: distance from shore and distance from port. We use
these as variables of interest and perform the following regression:

\[
y = \beta_1Year + \beta_2Treated + \beta_3Year \ Treated + \epsilon
\]

Where \(y\) is our variable of interest, \(Year\) represent year
dummies, with 2012 as the reference level, and \(Treated\) indicates
wether a vessel belongs to the treated or control group.

@@

\hypertarget{distance-from-shore}{%
\subsubsection{Distance from shore}\label{distance-from-shore}}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & distance\_from\_shore \\ 
\hline \\[-1.8ex] 
 Constant & 233,057.900$^{***}$ \\ 
  & (1,558.294) \\ 
  & \\ 
 year\_c2013 & $-$818.044 \\ 
  & (2,623.263) \\ 
  & \\ 
 year\_c2014 & 14,220.260$^{***}$ \\ 
  & (1,701.637) \\ 
  & \\ 
 year\_c2015 & 140,980.200$^{***}$ \\ 
  & (1,668.140) \\ 
  & \\ 
 year\_c2016 & 32,557.750$^{***}$ \\ 
  & (1,584.182) \\ 
  & \\ 
 year\_c2017 & 168,283.100$^{***}$ \\ 
  & (1,653.912) \\ 
  & \\ 
 treated & $-$11,371.280$^{***}$ \\ 
  & (1,688.879) \\ 
  & \\ 
 year\_c2013:treated & 62,899.900$^{***}$ \\ 
  & (3,274.205) \\ 
  & \\ 
 year\_c2014:treated & $-$17,499.020$^{***}$ \\ 
  & (1,834.090) \\ 
  & \\ 
 year\_c2015:treated & $-$34,356.840$^{***}$ \\ 
  & (1,821.587) \\ 
  & \\ 
 year\_c2016:treated & 72,512.980$^{***}$ \\ 
  & (1,739.976) \\ 
  & \\ 
 year\_c2017:treated & $-$62,350.120$^{***}$ \\ 
  & (1,805.322) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 4,937,666 \\ 
R$^{2}$ & 0.032 \\ 
Adjusted R$^{2}$ & 0.032 \\ 
Residual Std. Error & 297,128.600 (df = 4937654) \\ 
F Statistic & 14,649.360$^{***}$ (df = 11; 4937654) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} c} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
TRUE \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} c} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
TRUE \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

\hypertarget{distance-from-ports}{%
\subsubsection{Distance from ports}\label{distance-from-ports}}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:dist_port}Regression results for distance from shore} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & distance\_from\_port \\ 
\hline \\[-1.8ex] 
 Constant & 362.707$^{***}$ \\ 
  & (1.971) \\ 
  & \\ 
 year\_c2013 & 9.082$^{***}$ \\ 
  & (3.198) \\ 
  & \\ 
 year\_c2014 & 105.414$^{***}$ \\ 
  & (2.148) \\ 
  & \\ 
 year\_c2015 & 357.746$^{***}$ \\ 
  & (2.113) \\ 
  & \\ 
 year\_c2016 & 112.441$^{***}$ \\ 
  & (2.009) \\ 
  & \\ 
 year\_c2017 & 356.506$^{***}$ \\ 
  & (2.099) \\ 
  & \\ 
 treated & 149.653$^{***}$ \\ 
  & (2.249) \\ 
  & \\ 
 year\_c2013:treated & 26.366$^{***}$ \\ 
  & (4.125) \\ 
  & \\ 
 year\_c2014:treated & 50.808$^{***}$ \\ 
  & (2.453) \\ 
  & \\ 
 year\_c2015:treated & $-$151.268$^{***}$ \\ 
  & (2.422) \\ 
  & \\ 
 year\_c2016:treated & $-$49.445$^{***}$ \\ 
  & (2.311) \\ 
  & \\ 
 year\_c2017:treated & $-$252.334$^{***}$ \\ 
  & (2.390) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 4,937,666 \\ 
R$^{2}$ & 0.047 \\ 
Adjusted R$^{2}$ & 0.047 \\ 
Residual Std. Error & 391.757 (df = 4937654) \\ 
F Statistic & 22,351.480$^{***}$ (df = 11; 4937654) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:dist_port}Regression results for distance from shore} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} c} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
TRUE \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:dist_port}Regression results for distance from shore} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} c} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
TRUE \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

\hypertarget{rasterized-regions}{%
\subsubsection{Rasterized regions}\label{rasterized-regions}}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
\caption{\label{fig:unnamed-chunk-31}\label{fig:raster_rgn}Rasterized
regions. Each color (number) indicates a distinct region.}
\end{figure}
